---
title: "My attempt at organizing the optimization process of the BITH SDM"
author: "Victor Cameron"
date: "09/2021"
output: html_document
---

Here are presented the BITH SDM outputs for various parameter values. I test different options in the attempt to identify the **best model**. 

Different metrics are used to compare and select models when appropriate. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE, 
                      message = FALSE)
```

```{r dependencies, include=FALSE}
# Functions
source("/Users/victorcameron/Documents/Git/Metapop_ms/SDM/SDM_functions.R")

# Data
# # Rasterized BITH occurences for south of Québec
BITH <- data.table::fread("/Users/victorcameron/Documents/Git/Metapop_ms/data_clean/GRBI_rasterized.csv")

# # Explanatory variables
explana_dat <- data.table::fread("/Users/victorcameron/Documents/Git/Metapop_ms/SDM/explana_dat_df.csv")

# # Template
template <- raster::raster("/Users/victorcameron/Documents/Git/Metapop_ms/data_clean/templateRaster.tif")
```

```{r useful functions, include=FALSE}
#########################
# Function to test model 
#########################

model.elevBehavior <- function(model, explana_dat, ...){
    # Temperature gradient
    temp <- seq(from=min(explana_dat[["temp"]], na.rm = TRUE), to=max(explana_dat[["temp"]], na.rm = TRUE), length.out=100)
    temp2 <- temp^2

    # Fix other variables
    dat <- explana_dat[1:100,]
    dat$prec <- mean(explana_dat[["prec"]], na.rm = TRUE)
    dat$abie.balPropBiomass <- 0.8#mean(explana_dat[["abie.balPropBiomass"]], na.rm = TRUE)
    dat$abie.balBiomass <- 30#mean(explana_dat[["abie.balBiomass"]], na.rm = TRUE)
    dat$temp <- temp
    dat$temp2 <- temp2
    elev <- seq(500, 1200, by = 25)

    # Predict
    intensity <- list()
    for(i in 1:length(elev)){
    dat$elevation <- elev[i]
    intensity[[i]] <- predict(model, newdata = dat, type = "response")
    }

    # Cols
    colo <- colorRampPalette(c("grey90", "steelblue4", 
                            "steelblue2", "steelblue1", 
                            "gold", "red1", "red4"))(length(elev))

    # Plot prediction
    plot(y = log(intensity[[length(elev)]]), x = dat$temp, col = colo[length(elev)], ylab="log(intensity)", type="l", xlab = "Temperature (°C)", ...)
    polygon(x = c(min(explana_dat[["temp"]], na.rm = TRUE), -2, -2, min(explana_dat[["temp"]], na.rm = TRUE)),                           # X-Coordinates of polygon
        y = c(-10000, -10000, 10000, 10000),                             # Y-Coordinates of polygon
        col = rgb(211,211,211, max=255, alpha=127),
        border=rgb(211,211,211, max=255, alpha=127))   
    for(i in 1:(length(elev)-1)){
    lines(y = log(intensity[[i]]), x = dat$temp, col=colo[i])
    }
    legend(3.6, max(log(unlist(intensity))), legend = elev, fill = colo, ncol = 2, title = "Elevation (m)", bty = 'n', cex = 0.5)
}

model.biomassBehavior <- function(model, explana_dat, ...){
    # Temperature gradient
    temp <- seq(from=min(explana_dat[["temp"]], na.rm = TRUE), to=max(explana_dat[["temp"]], na.rm = TRUE), length.out=100)
    temp2 <- temp^2

    # Fix other variables
    dat <- explana_dat[1:100,]
    dat$prec <- mean(explana_dat[["prec"]], na.rm = TRUE)
    abie.balPropBiomass <- seq(0,1,le=8)
    dat$abie.balBiomass <- 30
    dat$temp <- temp
    dat$temp2 <- temp2
    dat$elevation <- 1000

    # Predict
    intensity <- list()
    for(i in 1:length(abie.balPropBiomass)){
    dat$abie.balPropBiomass <- abie.balPropBiomass[i]
    intensity[[i]] <- predict(model, newdata = dat, type = "response")
    }

    # Cols
    colo <- colorRampPalette(c("grey90", "steelblue4", 
                            "steelblue2", "steelblue1", 
                            "gold", "red1", "red4"))(length(abie.balPropBiomass))

    # Plot prediction
    plot(y = log(intensity[[length(abie.balPropBiomass)]]), x = dat$temp, col = colo[length(abie.balPropBiomass)], ylab="log(intensity)", type="l", xlab = "Temperature (°C)", ylim = c(min(log(unlist(intensity))),max(log(unlist(intensity)))), ...)
    polygon(x = c(min(explana_dat[["temp"]], na.rm = TRUE), -2, -2, min(explana_dat[["temp"]], na.rm = TRUE)),                           # X-Coordinates of polygon
        y = c(-10000, -10000, 10000, 10000),                             # Y-Coordinates of polygon
        col = rgb(211,211,211, max=255, alpha=127),
        border=rgb(211,211,211, max=255, alpha=127))   
    for(i in 1:(length(abie.balPropBiomass)-1)){
    lines(y = log(intensity[[i]]), x = dat$temp, col=colo[i])
    }
    legend(3.6, max(log(unlist(intensity)), na.rm=T), legend = round(abie.balPropBiomass,1), fill = colo, title = "propBiomass", bty = 'n', cex = 0.5)
}
```

## Base model

I start with the model I believe *a priori* to be the best. Based on expert knowledge (COSEWIC, 2009), I define an interaction between temperature and precipitation, and between fir biomass and proportional biomass. 

Fir biomass and proportional biomass hopefully capture the habitat preference of the BITH with abundance of fir and with the disturbed dense forests in regeneration.

I also select 1000000 pseudo-absences as Renner (2015) suggests to capture a maximum of the environmental conditions.

| Parameter   | Value |
| :---------- | :---- |
| Cov         | "temp * temp2 * prec + abie.balPropBiomass * abie.balBiomass" |
| nquad       | 1000000 |
| quadOverlay | TRUE |

```{r baseModel, echo=FALSE}
cov <- c("temp * temp2 * prec + abie.balPropBiomass * abie.balBiomass")

res <- SDM.glm(template=template,
                  BITH=BITH,
                  covariables = cov, 
                  pred = explana_dat,
                  nquad = 1000000,
                  quadOverlay = FALSE,
                  nquadWanted = FALSE)
baseModel <- res[["model"]]
summary(baseModel)
```

```{r baseModel behavior, echo=FALSE, eval=TRUE}
model.elevBehavior(baseModel, explana_dat)
```
```{r baseModel AUC, echo=FALSE}
SDM.AUC(baseModel, newdata=explana_dat, BITH=BITH, RL_cutoff = 0.05, template = template, plot_prediction = FALSE)
 ```

## What formulae is most appropriate?

```{r elev models, echo=FALSE}
# Elevation added to formulae
cov <- c("temp * temp2 * prec + elevation + abie.balPropBiomass * abie.balBiomass")

res <- SDM.glm(template=template,
                  BITH=BITH,
                  covariables = cov, 
                  pred = explana_dat,
                  nquad = 1000000,
                  quadOverlay = TRUE,
                  nquadWanted = FALSE)
elevModel <- res[["model"]]

# Elevation added in interaction with climate 
cov <- c("temp * temp2 * prec * elevation + abie.balPropBiomass * abie.balBiomass")

res <- SDM.glm(template=template,
                  BITH=BITH,
                  covariables = cov, 
                  pred = explana_dat,
                  nquad = 1000000,
                  quadOverlay = TRUE,
                  nquadWanted = FALSE)
elevIntModel <- res[["model"]]
```

```{r elev models AUC, echo=FALSE, eval=FALSE}
SDM.AUC(elevModel, newdata=explana_dat, BITH=BITH, RL_cutoff = 0.05, template = template, plot_prediction = FALSE)
SDM.AUC(elevIntModel, newdata=explana_dat, BITH=BITH, RL_cutoff = 0.05, template = template, plot_prediction = FALSE)
```

| Parameter   | baseModel | elevModel | elevIntModel |
| :---------- | :-------- | :-------- | :----------- |
| Cov         | "temp * temp2 * prec + abie.balPropBiomass * abie.balBiomass" | "temp * temp2 * prec + elevation + abie.balPropBiomass * abie.balBiomass" | "temp * temp2 * prec * elevation + elevation + abie.balPropBiomass * abie.balBiomass" |
| nquad       | 1000000 | 1000000 | 1000000 |
| quadOverlay | TRUE | TRUE | TRUE |
| AUC         | 0.7181 | 0.8602 | 0.866 |

### Model behavior

```{r elevation model behavior, echo=FALSE, eval=TRUE}
par(mfrow=c(2,3))
model.elevBehavior(baseModel, explana_dat, main="baseModel")
model.elevBehavior(elevModel, explana_dat, main="elevModel")
model.elevBehavior(elevIntModel, explana_dat, main="elevIntModel")

model.biomassBehavior(baseModel, explana_dat)
model.biomassBehavior(elevModel, explana_dat)
model.biomassBehavior(elevIntModel, explana_dat)
```

### Model summaries

```{r elevation model summaries, echo=TRUE, eval=TRUE}
summary(elevModel)
summary(elevIntModel)
```


## What about quadrature points?

I selected the best fitting model according to AUC, model behavior and AIC values (elevModel) to then select the best number of quadrature points.

Valavi (2021) argues that class overlap is among the most important issues in SDM estimation. At least with RF algorithms.

On the other hand, Renner (2015) says that the background points should sample the full environmental space, even where the species has been observed.

I will therefore select thebest fitted model between overlapping and non-overlapping quadrature points.

```{r quad models, echo=FALSE}
# Select the number of quadrature points with saturated model
set.seed(123)
n.quad = c(1000, 10000, 100000, 1000000, 5000000) 
cov <- c("temp * temp2 * prec + elevation + abie.balPropBiomass * abie.balBiomass")

# With overlap
    AUC = rep(NA, length(n.quad))
    nquadWanted = rep(NA, length(n.quad))

    for(j in seq_along(n.quad)){
    res <- SDM.glm(template=template,
                   BITH=BITH,
                   covariables = cov, 
                   pred = explana_dat,
                   nquad = n.quad[j], 
                   quadOverlay = TRUE,
                   nquadWanted = TRUE)
    model <- res[["model"]]
    assign(paste0("model_", j), model)

    ## Compute AUC
    AUC[j] <- SDM.AUC(model, newdata=explana_dat, BITH=BITH, RL_cutoff = 0.05, template = template, plot_prediction = FALSE)

    ## Save estimated number of quad. points
    nquadWanted[j] <- res[["nquadWanted"]]
    }

# Without overlap
    AUC_noOverlap = rep(NA, length(n.quad))
    nquadWanted_noOverlap = rep(NA, length(n.quad))

    for(j in seq_along(n.quad)){
    res <- SDM.glm(template=template,
                   BITH=BITH,
                   covariables = cov, 
                   pred = explana_dat,
                   nquad = n.quad[j], 
                   quadOverlay = FALSE,
                   nquadWanted = TRUE)
    model <- res[["model"]]
     assign(paste0("model_noOverlap_", j), model)

    ## Compute AUC
    AUC_noOverlap[j] <- SDM.AUC(model, newdata=explana_dat, BITH=BITH, RL_cutoff = 0.05, template = template, plot_prediction = FALSE)

    ## Save estimated number of quad. points
    nquadWanted_noOverlap[j] <- res[["nquadWanted"]]
    }
```

The estimated required number of quadrature point to achieve sufficient acurate estimates is computed as A) the maximum AUC and B) the estimation of the loglikelihood within a standard error of two of its true value (Renner 2015):

```{r nquad plot, echo=FALSE, eval=TRUE}
par(mfrow=c(2,2))
plot(n.quad, AUC, log = "x", type = "o", main = "overlap of quad. points")
plot(n.quad, AUC_noOverlap, log = "x", type = "o", main = "No overlap of quad. points")
plot(n.quad, n.quad/nquadWanted, log = "x", type = "o", main = "overlap")
plot(n.quad, n.quad/nquadWanted_noOverlap, log = "x", type = "o", main = "noOverlap")
```

```{r nquad behavior, echo=FALSE, eval=TRUE}
par(mfrow=c(3,4))
for(i in 1:5){
    model.biomassBehavior(get(paste0("model_",i)), explana_dat, main=paste0("model_",n.quad[i]))
    model.biomassBehavior(get(paste0("model_noOverlap_",i)), explana_dat, main=paste0("model_noOverlap_",n.quad[i]))
}
```


Printing the summary of the best fit model according to AUC:
```{r summary best model AUC, echo=FALSE, eval=TRUE}
if(max(AUC, na.rm=TRUE) > max(AUC_noOverlap, na.rm=TRUE)){
   cat("The best fitting model is with overlap of quadrature points with observations and with ", n.quad[which.max(AUC)], " quad. points\n")
    bestModel_AUC <- get(paste0("model_", which.max(AUC)))
    summary(bestModel_AUC)
}else{
    cat("The best fitting model is without overlap of quadrature points with observations and with ", n.quad[which.max(AUC_noOverlap)], " quad. points\n")
    bestModel_AUC <- get(paste0("model_noOverlap_", which.max(AUC_noOverlap)))
    summary(bestModel_AUC)
}
```

Printing the summary of the model showing the best ratio between estimated and realized quadrature points :

```{r summary best model nquadwanted, echo=FALSE, eval=TRUE}
if(max(n.quad/nquadWanted) > max(n.quad/nquadWanted_noOverlap)){
   cat("The model with the best predicted to realized ratio of quadrature points with overlap is with ", n.quad[which.max(n.quad/nquadWanted)], " quad. points\n")
    bestModel_nQuadWanted <- get(paste0("model_", which.max(n.quad/nquadWanted)))
    summary(bestModel_nQuadWanted)
}else{
    cat("The model with the best predicted to realized ratio of quadrature points without overlap is with ", n.quad[which.max(n.quad/nquadWanted_noOverlap)], " quad. points\n")
    bestModel_nQuadWanted <- get(paste0("model_noOverlap_", which.max(nquadWanted_noOverlap/n.quad)))
    summary(bestModel_nQuadWanted)
}
```


## Test for the best threshold value to set the range limit

Using AUC values to test the accuracy of the prediction against the observations, I test what the best intensity threshold is to set the range limit:

```{r best threshold, echo=FALSE, eval=TRUE}
RangeLimit <- c(0.001, 0.005, 0.01, 0.03, 0.05, 0.07, 0.09, 0.11, 0.15, 0.2, 0.5)
cutoff_AUC <- c()
cutoff_nQuadWanted <- c()
i=1
for (cutoff in RangeLimit){
    cutoff_AUC[i] <- SDM.AUC(bestModel_AUC, newdata=explana_dat, BITH=BITH, RL_cutoff = cutoff, template = template, plot_prediction = FALSE, main = paste0("AUC_", cutoff))
    cutoff_nQuadWanted[i] <- SDM.AUC(bestModel_nQuadWanted, newdata=explana_dat, BITH=BITH, RL_cutoff = cutoff, template = template, plot_prediction = FALSE, main = paste0("nQuadWanted_", cutoff))
    i=i+1
}
```

```{r cutoff plot, echo=FALSE, eval=TRUE}
par(mfrow=c(1,2))
plot(RangeLimit, cutoff_AUC, log = "x", type = "o", main = "AUC by RL cutoff for \nbestModel_AUC")
plot(RangeLimit, cutoff_nQuadWanted, log = "x", type = "o", main = "AUC by RL cutoff for \nbestModel_nQuadWanted")
```

Following Renner (2015), I define the best model as the closest one to the number of quad points wanted according to the likelihood estimation. 

```{r Best model, echo=TRUE, eval=FALSE}
# Best model
cov <- c("temp * temp2 * prec + elevation + abie.balPropBiomass * abie.balBiomass")

res <- SDM.glm(template=template,
                  BITH=BITH,
                  covariables = cov, 
                  pred = explana_dat,
                  nquad = 5000000,
                  quadOverlay = TRUE,
                  nquadWanted = FALSE)

# Best intensity cutoff value to set the breeding range limit
RL_cutoff <- 0.005
```

```{r plot best pred, echo=FALSE, eval=TRUE}
if(max(cutoff_AUC, na.rm=TRUE) > max(cutoff_nQuadWanted, na.rm=TRUE)){
    bestCutoff <- RangeLimit[which.max(cutoff_AUC)]
    SDM.AUC(bestModel_AUC, newdata=explana_dat, BITH=BITH, RL_cutoff = bestCutoff, template = template, plot_prediction = TRUE, points = TRUE, dev.new = FALSE, main = "best model")
}else{
    bestCutoff <- RangeLimit[which.max(cutoff_nQuadWanted)]
    SDM.AUC(bestModel_nQuadWanted, newdata=explana_dat, BITH=BITH, RL_cutoff = bestCutoff, template = template, plot_prediction = TRUE, points = TRUE, dev.new = FALSE, main = "best model")
}
```

